Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-02-16 ltx/data_paper/DataPaper.tex
edits to maximization
added note to discussion
fixed the conflict on exp for the distributions

\ifpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage{graphicx}
\fi
\usepackage{color}
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}

@@

@@

where $\sigma_W \ge 0$ is a measure of the introduced space-time randomness. For $\sigma_W = 0$ a pure deterministic process is recovered. As a result of the random component component, for $\sigma_W > 0$, the membrane voltage $v(\mathbf{r},t)$ is itself a stochastic process. Assuming an infinite propagation velocity for action potentials within the field, the deterministic incoming firing rate is described by a spatial convolution \red{citation?}

@@

where $v_0$ and $\varsigma$ describe the firing threshold the slope of the sigmoid respectively. 

@@

enables the pseudo inverse of $\boldsymbol{\phi(\mathbf{r})}$ to be taken, such that the state vector can is isolated on the left-hand-side as

@@

 p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \exp\left(-\frac{1}{2}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right) \\

@@

2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&=-n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right]  \\

@@

\begin{itemize}
	\item  
\end{itemize}

>>>>

\ifpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage{graphicx}
\fi
\usepackage{color}
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
\newcommand{\cyan}{\textcolor{cyan}}

@@

\cyan{small thing: are we using $\exp(x)$ or $e^x$ to represent exponential?}

@@

where $\sigma_W \ge 0$ is a measure of the introduced space-time randomness. For $\sigma_W = 0$ a pure deterministic process is recovered. As a result of the random component, for $\sigma_W > 0$, the membrane voltage $v(\mathbf{r},t)$ is itself a stochastic process. Assuming an infinite propagation velocity for action potentials within the field, the deterministic incoming firing rate is described by a spatial convolution \red{citation?}

@@

where $v_0$ and $\varsigma$ describe the firing threshold and the slope of the sigmoid respectively. 

@@

enables the pseudo inverse of $\boldsymbol{\phi(\mathbf{r})}$ to be taken, such that the state vector is isolated on the left-hand-side as

@@

 p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&= \mid\boldsymbol\Sigma_{\epsilon}\mid^{-\frac{1}{2}}  \exp\left({-\frac{1}{2}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)^\top\boldsymbol\Sigma_{\epsilon}^{-1}\left(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}\right)}\right),\\

@@

2\ln p\left(\mathbf y_{t+1}|\mathbf x_{t+1};\sigma_{\epsilon}\right)&=-n_y\ln \sigma_{\epsilon}^2-\frac{1}{\sigma_{\epsilon}^2}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\right],  \\

@@

\begin{itemize}
	\item comment on how the e step is ukf and m step is kinda like the ekf.  
\end{itemize}
